The influence of massive early merger events on the chemo-dynamics of galaxy discs

### 2022-10-13 src/tex/ms.tex
[showyourwork] overleaf sync

%%%%%%%%%%%%%%%%%% FIGURE 1 %%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\begin{center}
\begin{minipage}{.495\textwidth}
\centering
\includegraphics[width=\textwidth]{./plots/imf}
\end{minipage}
\begin{minipage}{.495\textwidth}
\centering
\includegraphics[width=\textwidth]{./plots/lifetime}
\includegraphics[width=\textwidth]{./plots/delay_time}
\end{minipage}
\end{center}
\vspace{-.35cm}
\caption{The simple stellar population model parameters: The stellar initial mass function (IMF, left panel), the stellar lifetime function (upper right panel) and the SNIa delay time distribution function (lower right panel). In the left panel we compare different IMFs as indicated in the legend. For each IMF the coloured numbers indicate the mass fraction of star above $8 \Msun$ up to the assumed maximum mass of $100 \Msun$. The upper right panel compares stellar lifetimes as a function of stellar mass for models from \citet{Argast2000} for three different metallicities with a model from \citet{Raiteri1996} at solar metallicity. Gray dashed lines indicate the lifetime of an $8 \Msun$ star. The lower right panel shows the empirical SNIa delay time distribution \citep{Maoz2010} with parameters taken from \citet{Maoz2012} and \citet{MaozMannucci2012}. Gray data points show the observational data taken from \citet{Maoz2012}.}
\label{fig:param1}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%%%%% FIGURE 1 %%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\begin{center}

\end{center}
\vspace{-.35cm}
\caption{}
\label{fig:param1}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
